Download data

### 2024-05-07 scripts/subsetDataforCrews.Rmd
fn tear down and restart

spp_needed <- read.csv('../data/raw/contract_lkp.csv') %>% 
  left_join(spp_needed, ., by = c('contract' = 'Contract_colloquial')) %>% 
  select(-contract) %>% 
  distinct()
```

@@

@@

lapply(seniors_list[3],  project_maker,
       admu = admin_boundaries, intype = 'senior',
       target_species = spp_needed, 
       blm_surf = blm_surf, 
       fs_surf = usfs_surf, 
       fire = fire_perimeters, 
       invasive = invasives, 
       total_change = change_intensity, 
       occurrences = occurrences, 
      # historic_SOS, 
       roads = roads, seed_transfer = STZ)

>>>>

spp_needed <- read.csv('../data/raw/contract_lkp.csv') %>% 
  left_join(spp_needed, ., by = c('contract' = 'Contract_colloquial')) %>% 
  select(-contract) %>% 
  distinct()

# add on the paths to their SDM's and post-processed SDMs

patches_p <- '/media/steppe/hdd/SDM_restorations/results/PatchesClippedBLM'
sdm_files <- file.path(patches_p, list.files(patches_p, pattern = 'shp$'))
sdm_files_basin <- data.frame(
  path_basins = sdm_files, 
  taxon = gsub('.shp', '', basename(sdm_files))
  )

raw_p <- '/media/steppe/hdd/SDM_restorations/results/suitability_maps'
sdm_files <- file.path(raw_p, list.files(raw_p, pattern = 'tif$'))
sdm_files <- sdm_files[grepl('1k-', sdm_files)]

sdm_files <- data.frame(
  path_raw_sdm = sdm_files, 
  taxon = gsub('1k.*$', '', basename(sdm_files))
  )

spp_needed <- left_join(spp_needed, sdm_files, by = c('binomial' = 'taxon')) %>% 
  left_join(., sdm_files_basin, by = c('binomial' = 'taxon')) %>% 
  mutate(
    occurrence_path = 
      '/media/steppe/hdd/SDM_restorations/data/raw/occurrence/combined_records/jittered_occurrences.shp')

rm(patches_p, sdm_files, sdm_files_basin, raw_p)
```

@@

emps <- filter(seed_zones, stz == 'DesertSW' & Requisition == 'Uncompahgre - P102085') %>% 
  pull(binomial) %>% 
  unique()

spp_needed_test <- filter(spp_needed, Requisition == 'Uncompahgre - P102085' & binomial %in% emps)
spp_needed_test <- split(spp_needed_test, f = spp_needed_test$binomial)

example_rast <- rast(spp_needed_test[[1]][,'path_raw_sdm'])
ptest <- project(prov_stz[[2]], 'epsg:5070')
ptest <- resample(ptest, example_rast)

#### Process geographic data to a mask of the field office ####
focal_bbox <- dplyr::filter(admin_boundaries, ADMU_NA %in% stringr::str_to_upper(teams_list[[13]]$FieldOffice) ) %>%  
  sf::st_union() %>% 
  sf::st_transform(5070)

focal_bbox <- focal_bbox 
blm_surf_sub <- sf::st_intersection(blm_surf, focal_bbox)

ptest <- mask(ptest, blm_surf_sub)
plot(ptest)

a <- lapply(X = spp_needed_test[1], FUN = empiricalSTZ_writer, seed_zones = seed_zones, pSTZs = ptest)

b <- vect(spp_needed_test[[1]][,'path_basins'])

ob <- terra::mask(b, ptest)

plot(a[["Aristida_purpurea"]])
```

```{r}
f <- system.file("ex/elev.tif", package="terra")
r <- rast(f)
msk <- ifel(r < 400, NA, 1)

m <- mask(r, msk)

f <- system.file("ex/lux.shp", package="terra")
v <- vect(f)[1,]

mv1 <- mask(r, v)
plot(mv1)
```

@@

lapply(seniors_list[3],  project_maker,
       admu = admin_boundaries, intype = 'senior',
       target_species = spp_needed, 
       blm_surf = blm_surf, 
       fs_surf = usfs_surf, 
       fire = fire_perimeters, 
       invasive = invasives, 
       total_change = change_intensity, 
       occurrences = occurrences, 
       roads = roads, seed_transfer = STZ)
